PineAPPL:\\ combining EW and QCD corrections for PDF fits

### 2020-08-17 paper/app-pineappl.tex
Add missing links to documentation

The following run card was used to produce the results shown in section~\ref{sec:dy-lepton-pair-production}.
The only difference with respect to a standard \textsc{mg5\_aMC} run is the switch \texttt{set iappl 1}, which enables to fill a \textsc{PineAPPL} grid.
For a complete set of runcards and patches see TODO.
\begin{verbatim}
set complex_mass_scheme True
import model loop_qcd_qed_sm_Gmu
define p = p b b~
define j = p
generate p p > e+ e- [QCD QED]
output @OUTPUT@
launch @OUTPUT@
fixed_order = ON
set mz @MZ@
set ymt @YMT@
set ebeam1 3500
set ebeam2 3500
set pdlabel lhapdf
set lhaid 324900
set fixed_ren_scale True
set fixed_fac_scale True
set mur_ref_fixed @MZ@
set muf_ref_fixed @MZ@
set reweight_scale True
set ptl = 25.0
set etal = 2.5
set mll = 116
#user_defined_cut set mmllmax = 1500.0
set req_acc_FO 0.0001
set iappl 1
done
quit
\end{verbatim}

@@

% TODO: link to documentation

@@

The following listing shows how to setup \textsc{PineAPPL} using its C interface in a simple Monte Carlo integrator for calculating the double-photon contribution to Drell--Yan lepton-pair production at the LHC.
All \textsc{PineAPPL} functions have the prefix \texttt{pineappl\_}.
The full example can be found at \url{https://github.com/N3PDF/pineappl/tree/master/examples/capi-dy-aa}.

>>>>

The following run card was used to produce the results shown in section~\ref{sec:dy-lepton-pair-production}.
The only difference with respect to a standard \textsc{mg5\_aMC} run is the switch \texttt{set iappl 1}, which enables to fill a \textsc{PineAPPL} grid.
For a complete set of runcards and patches see \url{https://n3pdf.github.io/pineappl}.
\begin{verbatim}
set complex_mass_scheme True
import model loop_qcd_qed_sm_Gmu
define p = p b b~
define j = p
generate p p > e+ e- [QCD QED]
output @OUTPUT@
launch @OUTPUT@
fixed_order = ON
set mz @MZ@
set ymt @YMT@
set ebeam1 3500
set ebeam2 3500
set pdlabel lhapdf
set lhaid 324900
set fixed_ren_scale True
set fixed_fac_scale True
set mur_ref_fixed @MZ@
set muf_ref_fixed @MZ@
set reweight_scale True
set ptl = 25.0
set etal = 2.5
set mll = 116
#user_defined_cut set mmllmax = 1500.0
set req_acc_FO 0.0001
set iappl 1
done
quit
\end{verbatim}

@@

@@

The following listing shows how to setup \textsc{PineAPPL} using its C interface in a simple Monte Carlo integrator for calculating the double-photon contribution to Drell--Yan lepton-pair production at the LHC.
All \textsc{PineAPPL} functions have the prefix \texttt{pineappl\_}.
The full example can be found at \url{https://github.com/N3PDF/pineappl/tree/master/examples/capi-dy-aa} and the full documentation of the C API can be found at \url{https://docs.rs/pineappl_capi}.
